---
title: "spotahome"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preliminary analysis

Preview of the data included in the dataframe

```{r dataload, include=FALSE}
library(DBI)
library(RSQLite)
library(dplyr)
library(tidyverse)
con <- dbConnect(SQLite(), "exercise_final.db")


as.data.frame(dbListTables(con))
 

access_log <- dbReadTable(con, 'access_log')
```
```{r preview, echo=FALSE}
print(summary(access_log))

dup_book_req <- access_log[access_log$event_type == "booking_request",]
revenue <- subset(dup_book_req, (dup_book_req$revenue <= 0) | is.na(dup_book_req$revenue))
print("Number of data with revenue 0 or NA")
print(nrow(revenue))

access_log1 <- anti_join(access_log,revenue, by = c("user_id", "variant"))
print("Number of current data in the dataset")
print(nrow(access_log1))
```

The first thing we can see is that revenue minimum value is 0.

After that, I am checking if there are data with revenue 0 or below and I delete it.

After that cleaning, we check that we have yet a user with duplicated booking request.
```{r revenue, echo=FALSE}
dup_book_req <- access_log1[access_log1$event_type == "booking_request",]
print("Number of booking request:")
print(nrow(dup_book_req))
print("Number of duplicated users:")
dup_user <- dup_book_req[duplicated(dup_book_req$user_id), ] 
print(nrow(dup_user))
print("It is an user with requests in both variants, as long as I have more data in variant A, I delete it from variant B")
access_log2 <- anti_join(access_log1,dup_user, by = c("user_id", "variant"))

```
Final check is if we have more users in both variants:

```{r variants, echo=FALSE}
user_var <- access_log2[,c("user_id", "variant")]

user_var_uni <- unique(user_var)

user_dup <- user_var_uni[duplicated(user_var_uni$user_id),]

log_dup <- filter(access_log2,
                       user_id %in% user_dup$user_id)

print(table(access_log2$variant))

print(table(log_dup$variant,log_dup$event_type))

print("I will delete the duplicated in the variant where they didn't made a booking request")

user_BR <- filter(log_dup, event_type == "booking_request")

user_delete <- anti_join(log_dup,user_BR, by =c("user_id", "variant"))

user_delete2 <- filter(user_delete,user_id %in% user_BR$user_id)

access_log3 <- anti_join(access_log2,user_delete2, by =c("user_id", "variant"))

user_var <- access_log3[,c("user_id", "variant")]

user_var_uni <- unique(user_var)

user_dup <- user_var_uni[duplicated(user_var_uni$user_id),]

log_dup <- filter(access_log3,
                       user_id %in% user_dup$user_id)

print(table(access_log3$variant))

print(table(log_dup$variant,log_dup$event_type))

print("Now we only have duplicated users without booking requests, more in the variant as total data is higher in variant A, I decide to delete them from there")

log_dup <- filter(access_log3,
                       user_id %in% user_dup$user_id & variant == "A")

access_log4 <- anti_join(access_log3,log_dup, by =c("user_id", "variant"))

user_var <- access_log4[,c("user_id", "variant")]

user_var_uni <- unique(user_var)

user_dup <- user_var_uni[duplicated(user_var_uni$user_id),]

print("We finally have no duplicated in the database:")

print(nrow(user_dup))

```
## Data Analysis CVR

Now we can start with the analysis of the data.

First working with conversion rate

Following I have done a proportion test and a chi-square test and both tell us that there is difference with 95% of confidence, but not at 99%

```{r cvr, echo=FALSE}
user_BR <- filter(access_log4, event_type == "booking_request")

access_log4$BR <- 0

access_log5 <- within(access_log4, BR[user_id %in% user_BR$user_id] <- 1)

Conv_rate <- unique(access_log5[c("user_id", "variant", "BR")])


control_sz<-length(which(Conv_rate$variant=="A"))
exp_sz<-length(which(Conv_rate$variant=="B"))
control_yes<-length(which(Conv_rate$variant=="A" & Conv_rate$BR=="1"))
exp_yes<-length(which(Conv_rate$variant=="B" & Conv_rate$BR=="1"))
prop.test(c (control_yes, exp_yes), c (control_sz, exp_sz), conf.level = 0.95)
prop.test(c (control_yes, exp_yes), c (control_sz, exp_sz), conf.level = 0.99)


ch_test<-chisq.test(Conv_rate$variant,Conv_rate$BR) #p-value < 0.05

ch_test$p.value

ch_test$stdres

```
## Data Analysis Revenue per user

With the revenue per user, we have to change the tests, because it is a continuous variable, and, running T test, we get statistically significant at 95%

```{r rpu, echo=FALSE}
library(broom)
rpu <- access_log5 %>% 
  group_by(user_id, variant) %>% 
  summarise_all(funs(sum(revenue, na.rm=TRUE))) 

mean_rpu <- access_log5 %>% 
  group_by(variant) %>% 
  summarise_all(funs(mean(revenue, na.rm=TRUE))) 

print(table(mean_rpu$variant, mean_rpu$revenue))

print("we hae that revenue is higher in variant B, as expected")

experiment_results <- t.test(revenue ~ variant,
                          data = rpu) %>%
  tidy()
print(experiment_results)

```

## Including Plots

You can also embed plots, for example:

```{r density, echo=FALSE}

log_A <- subset(rpu, variant == "A")
log_B <- subset(rpu, variant == "B")

density.A = density(log_A$revenue, na.rm = T)
density.B = density(log_B$revenue, na.rm = T)
# number of points used in density plot
n.density1 = density.A$n
n.density2 = density.B$n
# bandwidth in density plot
bw.density1 = density.A$bw
bw.density2 = density.B$bw
plot(density.B, main = 'Kernel Density Estimates of revenue', xlab = 'REVENUE', ylab = 'Density', ylim = c(0, max(density.A$y, na.rm = T)), lty = 1)
# add second density plot
lines(density.A, lty = 3)
# add legends to state sample sizes and bandwidths; notice use of paste()
legend(100, 0.015, paste('A: N = ', n.density1, ', Bandwidth = ', round(bw.density1, 1), sep = ''), bty = 'n')
legend(100, 0.013, paste('B: N = ', n.density2, ', Bandwidth = ', round(bw.density2, 1), sep = ''), bty = 'n')
# add legend to label plots
legend(115, 0.011, c('A', 'B'), lty = c(3,1), bty = 'n')
```

Revenue is concentrated at lower level in variant A


```{r avg, echo=FALSE}

avg_BR <- subset(access_log5, event_type == "booking_request")

avg_BR_agg <- avg_BR %>% 
  group_by(variant) %>% 
  select(variant, revenue) %>% 
  summarise_all(funs(mean,sd(., na.rm=TRUE))) 

print("Average and deviation")
print(avg_BR_agg)

print("Percentage increase")

print(diff(avg_BR_agg$mean)/avg_BR_agg$mean[1])

```
